### 2016-05-28 R/ITHIM.Rmd
Update to ITHIM.Rmd

```{r instantiate}
ITHIM.baseline <- list(
  parameters = parameters <- createParameterList(baseline = TRUE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
ITHIM.scenario <- list(
  parameters = parameters <- createParameterList(baseline = FALSE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
```
Now we can compute the attributable fraction (AF).

>>>>

```{r instantiate}
ITHIM <- list(
  parameters = parameters <- createParameterList(baseline = TRUE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
ITHIM.scenario <- list(
  parameters = parameters <- createParameterList(baseline = FALSE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
```
Now we can compute the attributable fraction (AF).
